SIPESCA-B: a set of real data time series benchmark for traffic prediction

### 2015-06-12 paper.tex
completando la secc <Conclusions>
arreglando el abstract

%********************************************************************************
\section{Conclusions and future work}

>>>>

%********************************************************************************
\section{Conclusions and Work in Progress}
\label{sec:Conclusions}

There are many fields, such as traffic management area, in which researchers have a need for standard benchmarks to be used with their prediction methods.
In fact, it is very difficult to obtain real data and even data in suitable or standard formats.

This paper presents the benchmark SIPESCA-B, a set of time series obtained monitoring the traffic at several locations of the road network \cite{papersipesca1,papersipesca2}.
Real data were obtained by monitoring BT or WiFi signals transmited by passing devices through several locations on highways, roads and streets along several months.

Data sets are left available to practitioners under the Open Database License in the public code repository 
{\tt https://github.com/Sipesca/Datasets}

The main objective is that SIPESCA-B serves as a standard benchmark and help researchers working in the traffic management area to test their prediction methods and to present their results, making them comparable and reproducible.

In this sense, a series of benchmark results is provided as a basis for comparisons.
In the experimental part of this work, several time series have been used and a study to predict short term (one day, the next 24 values) has been conducted; the objective is to determine the future traffic flow in each monitored location.
Three different prediction methods, validated in the literature, have been selected, and then, seven error measures have been calculated.

As Table \ref{tabla:errores} shows, the best overall prediction results were obtained using the SVM-MLP method.
In most cases, this method obtains lower error measurements when predicting considered time series.

Finally, this work opens up a range of possibilities for analyzing the large amount of collected data and to develop and implement methods of traffic flow prediction, not only short term but in the medium and long term. 
This could facilitate critical tasks in the traffic management area in monitored roads.

As future work, as new data is collected continuously, new more complete time series, covering longer time periods will be obtained. Thus, new data and new time series obtained will be left available in the public repository.
New prediction methods and tools will be used to forecast the time series, and obtained results using those methods will be published.
